QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`

### 2024-03-08 minos/outcomes/QALY_comparison2.Rmd
Parameterised the start year so we can handle synthetic 2020 starts alongside default 2020

---
params:
  experiment: ''
  base: ''
  intervention: ''
title: "QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r}
experiment <- params$experiment
baseline <- params$base
intervention <- params$intervention
# 
# experiment <- 'default_config'
# baseline <- 'baseline'
# intervention <- '50All'
```

@@

```{r}
ICER(base = base,
     base.name = baseline,
     int = int,
     int.name = intervention,
     QALY_value = 70000,
     int.label = intervention)
```

>>>>

---
params:
  experiment: ''
  base: ''
  intervention: ''
  start.year: ''
title: "QALY Comparisons - `r params$experiment` - `r params$intervention` - `r params$baseline`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r}
experiment <- params$experiment
baseline <- params$base
intervention <- params$intervention
start.year <- params$start.year
# 
# experiment <- 'default_config'
# baseline <- 'baseline'
# intervention <- '50All'
```

@@

```{r}
ICER(base = base,
     base.name = baseline,
     int = int,
     int.name = intervention,
     QALY_value = 70000,
     int.label = intervention,
     start.year = start.year)
```
